---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# roistats

<!-- badges: start -->
[![R-CMD-check](https://github.com/Irisfee/roistats/workflows/R-CMD-check/badge.svg)](https://github.com/Irisfee/roistats/actions)
[![Codecov test coverage](https://codecov.io/gh/Irisfee/roistats/branch/main/graph/badge.svg)](https://codecov.io/gh/Irisfee/roistats?branch=main)
<!-- badges: end -->

The goal of this package is for easily applying same t-tests/basic data description across several sub-groups, with the output as a nice arranged `data.frame` instead of the detailed listed information. Multiple comparison and the significance symbols are also provided.

This kind of analysis is commonly seen in ROI (Region-of-interest) analysis of brain imaging data. That's why the package is called `roistats`.

## Installation

You can install the released version of roistats from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("roistats")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Irisfee/roistats")
```

## Usage

### Get some basic description about the data
```{r setup}
library(roistats)
str(color_index)
head(color_index)
df_sem(color_index, color_index) 
```

### One-sample t-tests for all sub-groups

```{r}
t_test_one_sample(color_index, "color_index", mu = 0)
```

### With significance symbol as output

```{r, message = FALSE}
library(dplyr)
color_index_one_sample_t_with_sig <- color_index %>% 
  t_test_one_sample("color_index", mu = 0, p_adjust = c("bonferroni","fdr")) %>% 
  mutate(sig_origin_p = p_range(p))
knitr::kable(color_index_one_sample_t_with_sig, digits = 3)
```

### Two-sample t-tests for all sub-groups

```{r}
t_test_two_sample(color_index_two_sample, x = "color_effect", y = "group", paired = TRUE)
```
