---
title: "Get started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get_started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```
The goal of this package is to easily apply the same t-tests/basic data description across several sub-groups, with the output provided as a nice arranged `data.frame`. Multiple comparison and $p$-value significance symbols are also provided.

This kind of analysis is commonly seen in ROI (Region-of-interest) analysis of brain imaging data (hence the name of the package, **roistats**).

```{r setup}
library(roistats)
```
## Get some basic description about the data

The package comes with a data.frame called `color_index`, which is similar in format to what we might get after cleaning and wrangling ROI data. This data.frame contains the neural analysis result of the degree of *color memory sensitivity* at each brain region of each subject. The `color_index` data frame has three columns: 

* `subj_id`: identifies the subjects in the study. 
* `roi_id`: identifies the brain sub-region of interest for the analysis. We are interested in eight brain regions. Note that the combination of `subj_id` and `roi_id` uniquely identifies rows in the dataset.
* `color_index`: indicates how sensitive a certain brain region is to the memory of color for each subject/brain region combination. 

```{r example}
head(color_index)
```

Before we dive into the statistical test, we likely want to get descriptive statistics for `color_index`, including the mean, standard deviation, and standard error of the mean for each brain region. The `df_sem` function help us with this, and is designed to be used in combination with [**dplyr**](https://dplyr.tidyverse.org), specifically `dplyr::group_by()`. To obtain our descriptive statistics by `roi_id`, we just first group the data frame by `roi_id`, then pass the data frame to `def_sem()`. 

```{r message = FALSE}
library(dplyr)

color_index %>%
  group_by(roi_id) %>% # The column to get summaries by
  df_sem(color_index) # The column to summarize
```

Yay! We have obtained the `SEM` (which is commonly used for error bar plotting in psych and cog neuro area) for each sub-group easily.


Note that if we do not use `dplyr::group_by()` we just get the overall summaries. The package reports a warning when this happens because it generally goes against the intent of the package (computing multiple comparisons).

```{r warning = TRUE}
df_sem(data = color_index, x = color_index)
```


## One-sample t-tests for all sub-groups

Now suppose we want to test whether `color_index` is *significantly* different (i.e., significantly different than zero) for each possible sub-group (`roi_id`). Note that we are not computing pairwise comparisons yet, just whether the mean for each subgroup is different from zero. Here, we have eight sub-groups, which means we will get eight one-sample t-test results in total. As a first step in the analysis we probably don't care much about all the detailed output from `stats::t.test`. Instead, we're just looking for mean difference and significance. This is what the `t_test_one_sample` function was designed to accommodate. We again pass the function a grouped data frame, and we get $t$-test results back for each group. 

By default, a Bonferroni $p$-value adjustment is applied, but any adjustment available through `stats::p.adjust()` can be supplied. Similarly, each mean is compared to zero by default, but this can be adjusted through the optional `mu` argument. The interface for the function works essentially equivalanetly to `df_sem()`. 

```{r}
color_index %>% 
  group_by(roi_id) %>% 
  t_test_one_sample(color_index)
```

Here, we see the t-values, degrees of freedom, as well as the uncorrected and bonferroni corrected $p$-values! Nice! Note that the multiple comparison corrected $p$-values are provided by the `p_bonferroni` column, but the name of this column will change depending on the method you want to use. Let's try again, but this time using both the Bonferroni and the [Benjamini and Hochberg (1995)](https://www.jstor.org/stable/2346101?seq=1#metadata_info_tab_contents) method. We'll put this in a nice table as well.

```{r}
color_index_one_sample_t_res <- color_index %>%
  group_by(roi_id) %>% 
  t_test_one_sample(color_index, p_adjust = c("bonferroni", "BH"))

knitr::kable(color_index_one_sample_t_res, digits = 3)
```

As before, if we our data frame is not grouped, we'll get the stats returned, but with a warning.

```{r }
color_index %>% 
  t_test_one_sample(color_index)
```

## Significance symbols for an even clearer table and possible visulization

Usually, we want the significance symbol to highlight the result in a table or plot. Here we have the `p_range`
function to create the significance symbol:

```{r, message = FALSE}
color_index_one_sample_t_with_sig <- color_index_one_sample_t_res %>% 
  mutate(sig_origin_p = p_range(p))

knitr::kable(color_index_one_sample_t_with_sig, digits = 3)
```

You can use `p_range` for a single number too:

```{r}
p_range(0.002)
```

## Two-sample t-tests for all sub-groups

The `t_test_two_sample` function is used for applying two-sample t-tests to all sub-groups. This dataset has all the same columns as `color_index`, but also includes a `group` column specifying the condition of the experiement (paired versus control).

```{r}
head(color_index_two_sample)
```

We can obtain paired t-test for each sub-group using a similar approach as before. Here we're including the additional `paired = TRUE` argument to specify we want a paired $t$-test. This argument defaults to `FALSE`.

```{r}
color_index_two_sample %>% 
  group_by(roi_id) %>% 
  t_test_two_sample(color_effect, group, paired = TRUE)
```
